### 2022-04-19 GB_Simulation_3Species.Rmd
Added comment about rebuilding package for use on computer vs server

  library(MixFishSim) #each core needs to load library

>>>>

  #load rcpp exports ON SERVER ONLY. WONT WORK ON PC
Rcpp::sourceCpp(file= "src/Movement.cpp")
Rcpp::sourceCpp(file= "src/RcppExports.cpp")
Rcpp::compileAttributes() #this updates RcppExports.R file, which contains function definitions

  #ON PC JUST 1) REBUILD PACKAGE (ABOVE) THEN 2) RELOAD PACKAGE 
  library(MixFishSim) #each core needs to load library
